---
format: md
---

```{r}
#| echo: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "inst/extdata/"
)
```

## `gtm2`: Modeling Group Testing Data


###### Version : [`r getNamespaceVersion("gtm2")`](https://myaseen208.com/gtm2/); Copyright (C) 2024: License: [GPL-2|GPL-3](https://www.r-project.org/Licenses/)


##### *Muhammad Yaseen^1^, Christopher McMahan^1^*, Christopher Bilder^2^*, and Joshua Tebbs^3^*

1. [School of Mathematical & Statistical Sciences, Clemson University, Clemson, South Carolina, USA](https://www.clemson.edu/science/academics/departments/mathstat/)
2. [Department of Statistics, University of Nebraska-Lincoln, Nebraska, USA](https://www.chrisbilder.com/)
3. [Department of Statistics, University of South Carolina, Columbia, South Carolina, USA](https://people.stat.sc.edu/tebbs/)

***

[![minimal R version](https://img.shields.io/badge/R>%3D-3.5.0-6666ff.svg)](https://cran.r-project.org/)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version-last-release/gtm2)](https://cran.r-project.org/package=gtm2)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/gtm2?color=green)](https://CRAN.R-project.org/package=gtm2)
<!-- [![packageversion](https://img.shields.io/badge/Package%20version-0.2.3.3-orange.svg)](https://github.com/myaseen208/gtm2) -->

```{r}
#| results: asis
#| echo: false
#| eval: false
dver <- ifelse(test = gsub("(.\\.)(\\d+)(\\..)", "", getNamespaceVersion("gtm2")) != "",
               yes = getNamespaceVersion("gtm2"),
               no = gsub("Version:\\s*", "", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/gtm2", "/master/DESCRIPTION"))[grep("Version:", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/gtm2", "/master/DESCRIPTION")))]))
cat(paste("[![develVersion](https://img.shields.io/badge/devel%20version-", dver, "-orange.svg)](https://github.com/myaseen208/gtm2)", sep = ""))
```

<!-- [![GitHub Download Count](https://github-basic-badges.herokuapp.com/downloads/myaseen208/gtm2/total.svg)] -->
[![Project Status: WIP](https://www.repostatus.org/badges/latest/inactive.svg)](https://www.repostatus.org/#inactive)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](https://github.com/myaseen208/gtm2)
***

## Description
`r gsub("(<doi:)(.+)(>)", "[doi:\\2](https://doi.org/\\2)", gsub("\\n", " ", packageDescription("gtm2", fields = "Description")))`

## Installation
The package can be installed from CRAN as follows:

```{r}
#| eval: false
install.packages("gtm2")
```



The development version can be installed from github as follows:

```{r}
#| eval: false
library(pak)
pkg_install("myaseen208/gtm2")
```



## What's new
To know whats new in this version type:

```{r}
#| eval: false
news(package = "gtm2")
```

## Links

[CRAN page](https://cran.r-project.org/package=gtm2)

[Github page](https://github.com/myaseen208/gtm2)

[Documentation website](https://myaseen208.com/gtm2/)



To cite the methods in the package use:


```{r}
#| comment: ""
citation("gtm2")
```
